Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-02-25 Report/decomposition_solutions.tex
updated_lineno

Now, to decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which include all interference terms relevant for the transmission of \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method. Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through uplink sounding and the receive beamformers \me{\mvec{w}{l,k,n}}.

>>>>

To decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method. \R{who-knows-what}Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through precoded uplink sounding using the receive beamformers \me{\mvec{w}{l,k,n}} \cite{komulainen2013effective}. Each receiver is assumed to have the channel and the transmit precoders of all \acp{BS} in \me{\mc{B}} to evaluate \ac{MMSE} receiver.

### 2015-02-25 Report/review_comments.tex
updated_lineno

\resp We understand the reviewer concerns. We have modified the convergence section to include additional information to provide more clarity. Appendix \ref{sec-3.5} discuss the convergence proof of the proposed algorithm in detail.

@@

\resp We agree with the reviewers view. We have updated the convergence proof to include the discussions on the stationary point and the optimal point.

@@

\resp We thank the reviewer for the insightful comment on the practicality of the distributed algorithm. We fully agree with the reviewer comment on the information exchange between the BSs in the distributed approach. Please note that the proposed distributed algorithm based on the primal or dual decomposition is provided for the completeness purpose. Note that the distributed approach is performed for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution. In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which is not the stationary point when the algorithm is allowed to converge. In Section \ref{sec-4.3}, we have discussed a practical approach based on the KKT conditions, which attains a sub-optimal point with few number of iterations.

@@

\resp We understand the concern of the reviewer. We have updated the distributed section to include all the details pointed by the reviewer.

@@

\resp We understand the concern of the reviewer. We have updated the distributed section to include all the details pointed by the reviewer.

>>>>

\resp We understand the reviewer concerns. We have updated the convergence section to include additional information to provide more clarity. Appendix \ref{sec-3.5} discusses the convergence proof of the proposed algorithm in detail.

@@

\resp We agree with the reviewers view. We have updated the convergence proof for both centralized and distributed algorithm to include the discussions on the stationary point and the locally optimal point in Appendix \ref{sec-3.5} and Section \ref{sec-dist-conv}.

@@

\resp We thank the reviewer for the insightful comment on the practicality of the distributed algorithm. We fully agree with the reviewer comment on the information exchange between the BSs in the distributed approach. Please note that the proposed distributed algorithm based on the primal or dual decomposition is provided for the completeness purpose. Note that the distributed approach is performed for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution. In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which is not the stationary point when the algorithm is allowed to converge. In Section \ref{sec-4.3}, we have discussed a practical approach based on the KKT conditions, which attains a local optimal point with few number of iterations.

@@

\resp We understand the concern of the reviewer. We have updated the distributed section to include all the details pointed by the reviewer. Section \ref{sec-4.2} includes the updated discussions on ADMM scheme.

@@

\resp We understand the concern of the reviewer. We have updated the distributed section to include the details pointed by the reviewer. Section \ref{sec-4.2} includes the updated discussions on ADMM scheme. In addition, \lr{who-knows-what} includes information about who knows what in the network.
